Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

\subsection{Scope}
\label{sec:Scope}
The paper's focus lies on the scientific discussion of empirical test results. The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high-quality scientific paper. As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days. The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in the separate documentation paper.

@@

Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/). Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes. Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013). Kristoufek (2015) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term. However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency. Kristoufek (2015) further explains the correlation is most evident in the long run.  During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Kristoufek, 2015). These findings are in line with other researchers (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\

>>>>

\subsection{Scope}
\label{sec:Scope}
The paper's focus lies on the scientific discussion of empirical test results. The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high-quality scientific paper. As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days. The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in a separate documentation paper.

@@

Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/). Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for a means of payment. Even more, several authors argue that the Bitcoin price and transaction volumes are mainly driven by speculative investments rather than its actual use as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013). Kristoufek (2015) points out that there are other influencing factors such as its use in trade, the supply of currencies and price level, which all contribute to determining the Bitcoin price in the long term. However, according to the same author, evidence shows that investors’ interest plays an even greater role in bitcoin's price movements, and their correlation is even more evident in the long run, and during the periods of explosive increases or rapid declines of the price, investors’ interest accelerates the price movements (Kristoufek, 2015). These findings are in line with other research findings (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
